Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-04-07 4.exact_support_recovery/4.phase_transition_results.tex
added a remark
about the extra condition (4.9) right after the statement of Theorem 4.1.

\begin{theorem} \label{thm:sufficient}
Let the errors have common marginal distribution $F\in \text{AGG}(\nu)$ with $\nu>0$.  \stilian{If $\beta=1$, assume in addition that the
slowly varying function in \eqref{eq:sparsity-parametrized-new} is such that
\begin{equation}\label{e:new-beta=1-condition}
\ell(p) = o\Big(1/ F(- c\log(p)^{1/\nu})\Big),\ \ \mbox{ for all $c>0$.}
\end{equation}}{}
Let $\widehat{S}_p$ be the Bonferroni's procedure \eqref{eq:Bonferroni-procedure} with vanishing FWER $\alpha = \alpha(p) \to 0$, such that %\fbox{slower than any polynomial}
$\alpha p^\delta\to \infty$ for every $\delta>0$.
If
\begin{equation} \label{eq:signal-above-boundary}
    \underline{r} > f_{\mathrm{E}}(\beta) = (1 + (1 - \beta)^{1/\nu})^\nu,
\end{equation}
then we have
\begin{equation} \label{eq:exact-supporot-recovery}
    \lim_{p\to\infty}\sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p \neq S_p] = 0.
\end{equation}
\end{theorem}
\begin{proof}%[Proof of Theorem \ref{thm:sufficient}]
Throughout the proof, the dependence on $p$ will be suppressed to simplify notations when such omissions do not lead to ambiguity.

>>>>

\begin{theorem} \label{thm:sufficient}
Let the errors have common marginal distribution $F\in \text{AGG}(\nu)$ with $\nu>0$.  \stilian{If $\beta=1$, assume in addition that the
slowly varying function in \eqref{eq:sparsity-parametrized-new} is such that
\begin{equation}\label{e:new-beta=1-condition}
\ell(p) = o\Big(1/ F(- c\log(p)^{1/\nu})\Big),\ \ \mbox{ for all $c>0$.}
\end{equation}}{}
Let $\widehat{S}_p$ be the Bonferroni's procedure \eqref{eq:Bonferroni-procedure} with vanishing FWER $\alpha = \alpha(p) \to 0$, such that %\fbox{slower than any polynomial}
$\alpha p^\delta\to \infty$ for every $\delta>0$.
If
\begin{equation} \label{eq:signal-above-boundary}
    \underline{r} > f_{\mathrm{E}}(\beta) = (1 + (1 - \beta)^{1/\nu})^\nu,
\end{equation}
then we have
\begin{equation} \label{eq:exact-supporot-recovery}
    \lim_{p\to\infty}\sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p \neq S_p] = 0.
\end{equation}
\end{theorem}
\stilian{\begin{remark} The seemingly technical condition \eqref{e:new-beta=1-condition} is rather mild.
It is trivially satisfied if $\ell(p) \sim {\rm const}$.  This condition is only needed in the extremely sparse regime $\beta=1$.
\end{remark}}{}
\begin{proof}[Proof of Theorem \ref{thm:sufficient}]
Throughout the proof, the dependence on $p$ will be suppressed to simplify notations when such omissions do not lead to ambiguity.
